---
title: "Exercise 3 Solution"
format: docx
editor: visual
---

## Exercise 3

In RStudio, create a new Quarto document and do the following.

1.  Load the tidyverse.
2.  Import and explore `customer_data` using the functions we've covered.
3.  Provide at least one interesting numeric summary and one interesting visualization using discrete variables only.
4.  Practice good coding conventions: Comment often, write in consecutive lines of code using the `|>`, and use the demonstrated style (e.g., variable names, spacing within functions).
5.  Export the R script and upload to Canvas.

Five points total, one point each for:

\- Loading the tidyverse.

\- Providing at least one numeric summary.

\- Providing at least one visualization.

\- Following good coding conventions (provide feedback on this point).

\- Submitting an R script.

```{r}

# Load the tidyverse.

library(tidyverse)

# Import data.

customer_data <- read_csv("customer_data.csv", show_col_types = FALSE)

customer_data
```

```{r}

# At least one interesting numeric summary. For example, the number of "high income" customers by gender.

customer_data |> 
  mutate(high_income = income > 120000) |> 
  count(gender, high_income) |> 
  arrange(desc(n))
```

```{r}

# At least one interesting visualization. For example, the top 10 most commonly used words for 5-star reviews.

customer_data |>
  filter(star_rating == 5) |> 
  select(review_text) |> 
  tidytext::unnest_tokens(word, review_text) |> 
  drop_na(word) |> 
  anti_join(tidytext::stop_words) |> 
  count(word) |> 
  arrange(desc(n)) |> 
  slice(1:10) |> 
  mutate(word = fct_reorder(word, n)) |>
  ggplot(aes(x = n, y = word)) +
  geom_col() +
  labs(title = "Most Commonly Used Words for 5-Star Reviews")
```
